### 2020-08-31 code/figure4.Rmd
Fix error with figure 4

```{r forest-heatmap-data-plot, fig.align='center', fig.width= 9, fig.height= 8, message=FALSE}
#fig.width= 16, fig.height= 20,
load("../data/forest.heatmap.data.rda")

@@

all_compare_plot <- bind_rows(down_compare_plot, up_compare_plot)
all_compare_plot %<>% arrange(or, .by_group = TRUE) %>% mutate(Hugo_Symbol = as.character(Hugo_Symbol)) %>% ungroup() %>% mutate(Row_Index = sprintf("%3i", row_number()))
Hugo_rownames <- all_compare_plot$Hugo_Symbol
names(Hugo_rownames) <- as.character(all_compare_plot$Row_Index)
all_p <- ggplot(all_compare_plot, 
               aes(x = or,
                   y = Row_Index,down_compare_plot <- all_compare %>%
  group_by(cluster) %>%
  filter(or < 0) %>%
  filter(adjPval < 0.01) %>%
  arrange(-or) %>%
  filter(is.finite(or)) %>%
  slice_max(order_by = or, n = 10) %>%
  arrange(cluster, or, .by.group = TRUE)
down_compare_plot$Hugo_Symbol <- with(down_compare_plot,
                                      factor(as.character(Hugo_Symbol),
                                             levels = unique(as.character(Hugo_Symbol))))

@@

layout <- "ABB"
all_p + tdat_all_p + plot_layout(guides = 'collect', design = layout) & theme(legend.position = "bottom")
                   color = cluster,
                   group = cluster)) +
  geom_vline(xintercept = 0, linetype = 2) +
  geom_pointrange(aes(xmin = ci.low, xmax = ci.up)) +
  scale_y_discrete(labels = Hugo_rownames) +
  scale_color_manual(values = cluster_colors) +
  theme_classic() +
  xlab("log odds ratio") +
  ylab("Gene") +
  facet_grid(cluster ~ ., scales = "free_y", drop = TRUE, space = "free_y", switch = "y") +
  theme(
    panel.grid.major.y = element_line(colour = "#f0f0f0"),
    axis.title.y = element_blank()
  )

>>>>

```{r forest-heatmap-data-plot, fig.align='center', fig.width= 9, fig.height= 8, message=FALSE}
load("../data/forest.heatmap.data.rda")

@@

all_compare_plot <- bind_rows(down_compare_plot, up_compare_plot)
all_compare_plot %<>% arrange(or, .by_group = TRUE) %>% mutate(Hugo_Symbol = as.character(Hugo_Symbol)) %>% ungroup() %>% mutate(Row_Index = sprintf("%3i", row_number()))
Hugo_rownames <- all_compare_plot$Hugo_Symbol
names(Hugo_rownames) <- as.character(all_compare_plot$Row_Index)
all_p <- ggplot(all_compare_plot, 
               aes(x = or,
                   y = Row_Index,down_compare_plot <- all_compare %>%
  group_by(cluster) %>%
  filter(or < 0) %>%
  filter(adjPval < 0.01) %>%
  arrange(-or) %>%
  filter(is.finite(or)) %>%
  slice_max(order_by = or, n = 10) %>%
  arrange(cluster, or, .by.group = TRUE)))
down_compare_plot$Hugo_Symbol <- with(down_compare_plot,
                                      factor(as.character(Hugo_Symbol),
                                             levels = unique(as.character(Hugo_Symbol))))

@@
